|

### 2020-12-08 appendix/appendix.Rmd
Changes in appendix chunk sizes and typos.

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

@@

The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility. Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information. We decided which variables to keep by following the current practices of the literature. In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.

@@

@@

```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE}
dat %>%
  select(id, year) %>%
  unique() %>%
  ggplot(aes(x = as.factor(year))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", cache=TRUE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "Published Study?",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", cache=TRUE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "Electoral Systems",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", cache=TRUE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "Dependent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, cache=TRUE, fig.width=5, fig.height=4}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients") +
  theme_bw()
```

@@

```{r, cache=TRUE, fig.width=5, fig.height=4}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors") +
  theme_bw()
```

@@

```{r, fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE}
dat %>%
  ggplot(aes(x=as.factor(scoef))) +
  geom_bar(color = "black") +
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

@@

```{r, warning=F,message=F, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2 == "N")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2 == "logN")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, cache=TRUE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

@@

```{r, cache=TRUE}
# Pooling effects analysis -- logExpPC x N (RDD only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

@@

```{r, warning=F, cache=T}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, warning=F, cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, warning=F, cache=TRUE}
# Pooling effects analysis -- logExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, warning=F, cache=TRUE}
# Pooling effects analysis -- logExpPC x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

@@

```{r, warning=F, cache=TRUE}
# Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

@@

```{r, warning=F, cache=TRUE}
# Pooling effects analysis -- PCTGDP x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

@@

```{r, warning=F, cache=TRUE}
# Pooling effects analysis -- PCTGDP x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

@@

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

@@

```{r, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)
summary(mod)
```

@@

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, error=F, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))
summary(mod)
```
As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, error=F, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F, iter = 100)
mod
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)
```

```{r, warning=F, cache=T}
summary(mod)
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)
summary(mod)
```

@@

```{r, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
              test = "knha")
```

```{r}
summary(mod)
```

@@

```{r, cache=T}
permutest(mod, progbar = F)
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
              test = "knha")
```

```{r, cache=T}
summary(mod)
```

```{r, cache=T}
permutest(mod, progbar = F)
```

@@

```{r, eval = FALSE, cache=T}
# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect", "Prediction Interval"),
                lower = c(mod$lower.random, mod$lower.predict),
                upper = c(mod$upper.random, mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

@@

```{r, eval = FALSE, cache=T}
# Required packages
pkgs <- c("tidyverse", "rvest", "RSelenium")

@@

```{r}
sessionInfo()
```

>>>>

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

@@

The third phase consisted of filling out tables for each of the remaining 47 articles to systematically evaluate their eligibility. Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information. We decided which variables to keep by following the current practices of the literature. In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.

@@

If a paper did not use a combination of these variables, we excluded it from the meta-analysis.

@@

```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE, size="footnotesize"}
dat %>%
  select(id, year) %>%
  unique() %>%
  ggplot(aes(x = as.factor(year))) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", size="footnotesize", cache=TRUE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "Published Study?",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) +
    geom_bar(color = "black") +
  labs(x = "Electoral Systems",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "Dependent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", cache=TRUE}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
                                                  "N (lower house legislators)",
                                                  "Log N"))) %>%
  ggplot(aes(x = indepvar2)) +
    geom_bar(color = "black") +
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients") +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors") +
  theme_bw()
```

@@

```{r, size="footnotesize", fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE}
dat %>%
  ggplot(aes(x=as.factor(scoef))) +
  geom_bar(color = "black") +
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

@@

```{r, size="footnotesize", warning=F,message=F, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

@@

```{r, size="footnotesize", cache=TRUE}
aux <- filter(dat, indepvar2 == "N")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, size="footnotesize", cache=TRUE}
aux <- filter(dat, indepvar2 == "logN")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, size="footnotesize", cache=TRUE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

@@

```{r, cache=TRUE, size="footnotesize"}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- logExpPC x N (RDD only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

@@

```{r, size="footnotesize", warning=F, cache=T}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, size="footnotesize", warning=F, cache=TRUE}
# Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

@@

```{r, size="footnotesize", warning=F, cache=TRUE}
# Pooling effects analysis -- logExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

@@

```{r, size="footnotesize", warning=F, cache=TRUE}
# Pooling effects analysis -- logExpPC x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

@@

```{r, size="footnotesize", warning=F, cache=TRUE}
# Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

@@

```{r, size="footnotesize", warning=F, cache=TRUE}
# Pooling effects analysis -- PCTGDP x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

@@

```{r, size="footnotesize", warning=F, cache=TRUE}
# Pooling effects analysis -- PCTGDP x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

@@

```{r, size="footnotesize", cache=TRUE}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

@@

```{r, size="footnotesize", warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)
summary(mod)
```

@@

```{r, size="footnotesize", warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, size="footnotesize", warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, size="footnotesize", warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, size="footnotesize", error=F, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))
summary(mod)
```
As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, size="footnotesize", error=F, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, size="footnotesize", warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, size="footnotesize", warning=F, cache=T}
mod <- permutest(mod, progbar = F, iter = 100)
mod
```

@@

```{r, size="footnotesize", warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)
summary(mod)
```

@@

```{r, size="footnotesize", warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)
summary(mod)
```

@@

```{r, size="footnotesize", warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
              test = "knha")
summary(mod)
```

@@

```{r, size="footnotesize", cache=T}
permutest(mod, progbar = F)
```

@@

```{r, size="footnotesize", warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
              test = "knha")
summary(mod)
```

```{r, size="footnotesize", cache=T}
permutest(mod, progbar = F)
```

@@

```{r, size="footnotesize", eval = FALSE, cache=T}
# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect", "Prediction Interval"),
                lower = c(mod$lower.random, mod$lower.predict),
                upper = c(mod$upper.random, mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

@@

```{r, size="footnotesize", eval = FALSE, cache=T}
# Required packages
pkgs <- c("tidyverse", "rvest", "RSelenium")

@@

```{r, size="footnotesize"}
sessionInfo()
```
